Implementation of Concurrent Hash Tables in Java

### 2022-04-29 paper.tex
Finished Paper (hopefully)

@@

>>>>

The source code shown in "Listing 4" contains the \verb|put()| method for a fine-grain locking hash table. This method resembles the
\verb|put()| method for the coarse-grain locking hash table, but differs in a few key ways. The first notable difference is the lack of 
the \verb|syncrhonized| keyword in the method declaration. This means a call to this method would not block other threads from calling the
method until the call finishes. Rather, this method implements the use of locks to block threads at the critical sections of the code, the
critical section being the writing of the item into the hash table. What this code does is check to see if the memory location that the 
data will be stored in is null, and then acquires the lock for that location. Once the lock is acquired, the method checks once again that
memory location is null to ensure no other calls to the method wrote data in the time between checking and acquiring the lock. Once the data
is added to the hash table, the lock will be relinquished and other thread will be able to continue with their method calls. The only other
notable difference between the coarse-grain and fine-grain methods is that the fine-grain one utilizes quadratic probing.

@@

The fine-grain \verb|search()| method is once again notably similar to its coarse-grain counterpart. The only difference between the two
is difference in probing methods. The reasoning behind this is that since search only reads data from the array and does not write any,
there is no reason for it to acquire a lock at any point in its runtime. The program has no reason to block access to the memory location
in order to read it, and if data was being written to the memory location during the call to \verb|search()| then search would be blocked
by \verb|put()| or \verb|remove| acquiring the lock to that memory location.
